Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-03 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: corner plot
hs: which eft subset we work with

More specifically, we follow Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up
to dimension-eight operators (i.e., $n=4$),
%
\begin{subequations}
\label{eq:action_mods}
\begin{align}
    L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
    \nonumber \\
            &\quad + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
    \label{eq:s_6}
    \\
    L^{(8)} &= \varepsilon_{1} \mathcal{C}^2
    + \varepsilon_{2} \tilde{\mathcal{C}}^{2}
    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
\label{eq:s_8}
\end{align}
\end{subequations}
%
where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.

@@

@@

The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including (independently) its ringdown properties, using the Bayesian formalism above. Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger part of the signal. The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis. In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}. These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are extremely similar in their source properties. These are also two of the loudest BBH signals observed to date with a total network SNR of XX and XX respectively. Moreover, and what is more relevant for our analysis, is their post-inspiral (merger-ringdown) SNRs, which at XX and XX respectively (see the columns for $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and Table IV of ~\cite{LIGOScientific:2021sio}). In this paper, we are going to focus on these two GW events as our probes of the BH ringdown in modified theories of gravity.

@@

>>>>

More specifically, we follow Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up
to dimension-eight operators (i.e., $n=4$),
%
\begin{subequations}
\label{eq:action_mods}
\begin{align}
    L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
    % \nonumber \\
    %         &\quad
    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
    \label{eq:s_6}
    \\
    L^{(8)} &= \varepsilon_{1} \mathcal{C}^2
    + \varepsilon_{2} \tilde{\mathcal{C}}^{2}
    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
\label{eq:s_8}
\end{align}
\end{subequations}
%
where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.

@@

Here we will consider $\lame = \lamo = 1$ for simplicity in the cubic EFT, while in quartic,
we will $\varepsilon_{1} = 1$ and $\varepsilon_{1,\,2} = 0$. This is the same subset of the EFT's parameter
space studied in~\cite{Sennett:2019bpc}.

@@

The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
\emph{IMR} model which infers the properties of the underlying GW signal,
including (independently) its ringdown properties, using the Bayesian formalism
above. Naturally, the most promising candidates for our analyses are high-mass
\emph{and} loud GW observations with a significant signal-to-noise ratio (SNR)
in the post-merger part of the signal.
%
The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
signals not all of which are relevant for a BH ringdown analysis. In fact, in
an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
analysis\footnote{See, in particular, Sec.VIII A.2
in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
presented in this paper, identified two events which provided the strongest
bounds on measurements of the dominant $(220)$ QNM --
GW150914~\cite{LIGOScientific:2016aoc} and
GW200129~\cite{LIGOScientific:2021djp}.
%
These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
extremely similar in their source properties. These are also two of the loudest
BBH signals observed to date with a total network SNR of XX and XX
respectively.
%
Moreover, and what is more relevant for our analysis, is their post-inspiral
(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
Table IV of~\cite{LIGOScientific:2021sio}).
%
In this paper, we are going to focus on these two GW events as our probes of
the BH ringdown in modified theories of gravity.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/tmp_corner_plot.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$ and remnant mass $M_f$
in our non-GR parameter estimation run is consistent with an equivalent GR run.~\hs{Complete.}}
\label{fig:corner_plot}
\end{figure}
